Back to Normal Transits for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-04-13 ms.tex

% manuscript produces a one-column, double-spaced document:
%\documentclass[12pt,preprint]{aastex}
\documentclass[preprint]{aastex61_mod}
%\documentclass[iop]{emulateapj}

@@

@@

%\begin{abstract}
%KIC 12557548 b is one of several disintegrating planet candidates which lose mass in the form of dust particles escaping their surface. Photometric monitoring of KIC 12557548 b originally showed evidence for a slowdown of integration activity in 2013 and 2014. Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.
%We also examine the system with high resolution spectroscopy and discuss the parameters of the host star.
%\end{abstract}

@@

\section{Abstract}
KIC 12557548 b is one of several disintegrating planet candidates which lose mass in the form of dust particles escaping their surface. Photometric monitoring of KIC 12557548 b originally showed evidence for a slowdown of integration activity in 2013 and 2014. Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.
We also examine the system with high resolution spectroscopy and discuss the parameters of the host star.

@@

Subsequently, \citet{schlawin2016kic1255} observed 8 total transits of the system for 4 nights in 2013 and 4 nights in 2014 for the $r'$ band using the MORIS imager \citep{Gulbis2011} on SpeX/IRTF \citep{rayner03}.
\citet{schlawin2016kic1255} found that the transit depths were all weaker than $0.43\%$ and that the probably of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
This was evidence that the observations occured during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
We performed follow-up $R$ band photometry of the \shStar\ system to explore whether the disintegration activity was decreasing as a function of time.
We also analyze high resolution spectroscopy of the system to help resolve some of the different stellar parameters reported in the literature.

\section{Observations}
We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory on UT dates 2016-06-12, 2016-06-14, 2016-07-12, 2016-07-14, 2016-07-16.
The nights were clear with the exception of a few passing cloud son 2016-07-14.
We also attempted photometry on 2016-06-10, but clouds prevented precision time series.
We obtained photometry for 5 nights with good weather on the \sha\ system.

\subsection{Previous Observations}

In order to understand the long term behavior of the \sha\ system, we summarize the available published photometry in Table \ref{tab:prevObs}
The Kepler mission provided the longest time baseline with near continuous photometry for about 4 years in long cadence ($\sim$30 min) mode.
Following the failure of the reaction wheel, there were a few follow-up ground based observations.
\citet{bochinski2015evolving} obtained multi-color simultaneous photometry ($u'$, $g'$ and $z'$) to characterize the dust in the system.
The ratio of the $g'$ to $z'$ transit depths indeed deviated from unity, which could be fit with an interstellar dust extinction law.
Overall, \citet{bochinski2015evolving} observed 5 separate nights spanning the expected transit durations and detect 1 transit $\sim$1\% in $g'$ band, 1 transit $\sim$0.1\% in $g'$ band and 3 upper limits of < 0.03\% for the other nights.

For one of the flux dip events, the $g$ band photometry exhibited a deeper transit depth than the $z'$ band.
The ratio

\begin{deluxetable*}{lrrrr}
\tablecaption{List of published observations}\label{tab:prevObs}
\tablewidth{0pt}
\tablehead{
\colhead{Date Start} &
\colhead{Date End} &
\colhead{Observatory} &
\colhead{Filter} &
\colhead{Reference(s)} \\
UT & UT & & & \\
 }
\startdata
2009-05-13 & 2013-05-11 & Kepler & Open CCD & \citet{borucki2010} \\
2013-07-14 & 2013-07-31 & William Herchel & $u'$, $g'$, $z'$/$i'$ & \citet{bochinski2015evolving} \\
2013-08-13 & 2013-09-03 & IRTF & $r'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
2014-08-14 & 2013-09-04 & IRTF & $r'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
2016-06-12 & 2016-06-12 & Kuiper & Harris R & This Work \\
2016-07-12 & 2016-07-16 & Kuiper & Harris R & This Work \\
\enddata
\tablenotetext{}{Summary of published photometric observations of \sha.}
\end{deluxetable*}

@@

For the photometric reduction, we used the \texttt{ccdproc} package to generate master flat field and bias files.
I combined with an average with a low threshold of 2$\sigma$ and a high threshold of 5$\sigma$.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/figure_index_152.pdf}
\includegraphics[width=0.5\textwidth]{images/stamps_kic1255_UT2016_07_14.pdf}
\caption{Target (src) and reference stars (numbered) used on UT 2016-07-14.
The reference stars were chosen to have similar count levels as the source. 
}\label{fig:ut2016-07-14cloudImg}
\end{centering}
\end{figure}

All nights light curves are shown in Figure \ref{fig:allNightallStar}.
These are the same reference stars shown in Figure \ref{fig:ut2016-07-14cloudImg}.
The nights two nights in June, 2016 show greater overall stability than the ones in July, 2016.
I suspect that this can mostly be explained by moisture and clouds (such as the ones that caused huge drops in flux on UT2016-07-14.

\begin{figure*}
\begin{centering}
\includegraphics[width=0.9\textwidth]{images/all_kic1255_phot/all_kic1255_allstar.pdf}
\caption{Time series photometry for all stars and all nights nights.
The nights in July appear more strongly affected by cloud/and or seeing variations, whereas the two nights in June are stable to within a few percent.
All source radius, background start and background annulus end parameters were 9, 9 and 12 pixels respectively.}\label{fig:allNightallStar}
\end{centering}
\end{figure*}

Figure \ref{fig:allNightrefCorrect} shows the reference-corrected time series for \shStar\ showing transits.
We use the following planet transit ephemeris, using the flux minimum from Kepler data \citep{schlawin2016kic1255} and the orbital period from \citet{vanWerkhoven2014}.
\begin{equation}
T = T_0 + n P
\end{equation}
where $T_0 = 2454833.039$ BJD$_{TDB}$ and $P = 0.653 553 8 \pm 0.000 000 1$ days.

>>>>

% manuscript produces a one-column, double-spaced document:
%\documentclass[12pt,preprint]{aastex}
\documentclass[preprint]{aastex61}
%\documentclass[iop]{emulateapj}

@@

\author{Kento Masuda?}
\affiliation{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}

\author{Teruyuki Hirano?}
\affiliation{Department of Earth and Planetary Sciences, Tokyo Institute of Technology, Tokyo 152-8550, Japan}

\author{Hajima Kawahara?}
\affiliation{Department of Earth and Planetary Science, The University of Tokyo, Tokyo 113-0033, Japan;}

@@

\begin{abstract}
KIC 12557548 b is one of several disintegrating planet candidates which lose mass in the form of dust particles escaping their surface.
Photometric monitoring of KIC 12557548 b originally showed evidence for a slowdown of integration activity in 2013 and 2014.
Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.
We also evaluate high resolution spectra from the Subaru HDS spectrograph and find spectra consistent with a main-sequence T=4500 K, main-sequence star.
\end{abstract}

@@

%\section{Abstract}

@@

Subsequently, \citet{schlawin2016kic1255} observed 8 total transits of the system for 4 nights in 2013 and 4 nights in 2014 for the $r'$ band using the MORIS imager \citep{Gulbis2011} on SpeX/IRTF \citep{rayner03}.
\citet{schlawin2016kic1255} found that the transit depths were all weaker than $0.43\%$ and that the probably of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
This was evidence that the observations occurred during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
We performed follow-up $R$ band photometry of the \shStar\ system to explore the second hypothesis: that the disintegration activity decreases as function of time.

\section{Observations}
We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory on UT dates 2016-06-12, 2016-06-14, 2016-07-12, 2016-07-14, 2016-07-16.
The nights were clear with the exception of a few passing clouds on 2016-07-14.
We also attempted photometry on 2016-06-10, but clouds prevented precision time series.

@@

For the photometric reduction, we used the \texttt{ccdproc} package to generate master flat field and bias files.
They were combined with an average with a low threshold of 2$\sigma$ and a high threshold of 5$\sigma$.
12 stable reference stars with similar R band brightnesses were used to construct a reference time series to correct for variable telluric and instrument throughput.
These 12 reference stars' time series were combined with a weighted average and this combined time series was divided into the target, \sha.

Figure \ref{fig:allNightrefCorrect} shows the reference-corrected time series for \shStar\ for all 5 nights which were timed with transits.
We use the following planet transit ephemeris, using the flux minimum from Kepler data \citep{schlawin2016kic1255} and the orbital period from \citet{vanWerkhoven2014}.
\begin{equation}
T = T_0 + n P
\end{equation}
where $T_0 = 2454833.039$ BJD$_{TDB}$ and $P = 0.653 553 8 \pm 0.000 000 1$ days.
